### 2022-08-18 ersteops/templates/printpdf/rendered_template.tex
update templates

\begin{document}
\fontfamily{lmss}\selectfont
    % Include Background in ./prescript/media/media/template_v1.pdf
    % \AddToShipoutPictureBG{\ifthenelse{\isodd{\value{page}}}{\includegraphics{laam_template}}{\includegraphics{laam_template}}}
    % Define page content
    %\textsf{\large{
    %\begin{changemargin}{1.5cm}{1.2cm}
        %\begin{enumerate}
            %
            %bla!
        %\end{enumerate}
    %         \put(1,1){\parbox[t]{3cm}{\textsf{\large{
    %    \textbf{Consulta \#:} 34
    % }
    % }}}
        % Indicaciones Extra
        % \begin{enumerate}
        %     \textbf{Indicaciones Extra: \\ } 
        % \end{enumerate}
    %\end{changemargin}
    %}}
    % \begin{picture}(1,0.77272727)%
    %     %Consulta    
    % \put(200,0){\parbox[t]{3cm}{\textsf{\large{
    %    \textbf34
    % }
    % }}}
    % \end{picture}
% \begingroup%
%   \makeatletter%
%   \providecommand\color[2][]{%
%     \errmessage{(Inkscape) Color is used for the text in Inkscape, but the package 'color.sty' is not loaded}%
%     \renewcommand\color[2][]{}%
%   }%
%   \providecommand\transparent[1]{%
%     \errmessage{(Inkscape) Transparency is used (non-zero) for the text in Inkscape, but the package 'transparent.sty' is not loaded}%
%     \renewcommand\transparent[1]{}%
%   }%
%   \providecommand\rotatebox[2]{#2}%
%   \newcommand\scaleInNode[1][1]{\tikzset{execute at begin node={\normalsize\larger[#1]}}}
%   \newcommand*\fsize{\dimexpr\f@size pt\relax}%
%   \newcommand*\lineheight[1]{\fontsize{\fsize}{#1\fsize}\selectfont}%
%   \ifx\svgwidth\undefined%
%     \setlength{\unitlength}{792bp}%
%     \ifx\svgscale\undefined%
%       \relax%
%     \else%
%       \setlength{\unitlength}{\unitlength * \real{\svgscale}}%
%     \fi%
%   \else%
%     \setlength{\unitlength}{\svgwidth}%
%   \fi%
%   \global\let\svgwidth\undefined%
%   \global\let\svgscale\undefined%
%   \makeatother%
%   \begin{picture}(1,0.77272727)%
%     \lineheight{1}%
%     \setlength\tabcolsep{0pt}%
%     \put(0,0){\includegraphics[width=\unitlength,page=1]{laam_template}}%

%     % \put(0.01140896,0.54355203){\parbox[t]{3cm}{\textsf{\large{
%     %    \textbf{Consulta \#:} 34
%     % }
%     % }}}
%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 34 }\end{tabular}}}}%
% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 34 }\end{tabular}}}}%
%    	\put(0.42718184,0.72336542){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ M011 }\end{tabular}}}}%
%     \put(0.3690564,0.69389968){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ ASISTENCIA BASICA }\end{tabular}}}}%
%     \put(0.39254546,0.6775768){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ QPR-001 }\end{tabular}}}}%

@@

    \put(0.42638971,0.73960084){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 11\end{tabular}}}}%
    \put(0.43014479,0.72364315){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont M011\end{tabular}}}}%
   	\put(0.33829987,0.69381105){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont ASISTENCIA BASICA\end{tabular}}}}%
    \put(0.39132267,0.67728521){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont QPR-001\end{tabular}}}}%

    %Paciente
    \put(0.09655761,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont F55\end{tabular}}}}%
    \put(0.20912356,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 5556782349\end{tabular}}}}%
    \put(0.3268484,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Femenino\end{tabular}}}}%
    \put(0.42764439,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 45\end{tabular}}}}%
    \put(0.12766308,0.61324599){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Nika Sanchez Jaime\end{tabular}}}}%
    \put(0.02575936,0.58169366){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont luiis spota\end{tabular}}}}%

    %Paciente desconocido
    \put(0.01999075,0.53033139){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont paciente desconocido y asi\end{tabular}}}}%
    \put(0.01999075,0.48794778){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont  la filiacion desconocida\end{tabular}}}}%
    \put(0.09106678,0.46594263){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont pantalon rojo rotio\end{tabular}}}}%
    \put(0.12588643,0.44615019){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont rojo rojo amarillo\end{tabular}}}}%

    %Padecimiento
    \put(0.0159714,0.1825995){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont sdf sdfsdf sdf sdfsd fsd\end{tabular}}}}%
    %\put(0.02265882,0.24439213){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont sdf sdfsdf sdf sdfsd fsd\end{tabular}}}}%

    %Generales
    \put(0.12027596,0.41209986){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Hogar \end{tabular}}}}%
    \put(0.30209431,0.41082061){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Urgencias \end{tabular}}}}%
    \put(0.30209431,0.39566916){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Traumaticos \end{tabular}}}}%
    \put(0.21257984,0.38532216){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont [\textquotesingle Craneal\textquotesingle , \textquotesingle Craneoencefalico\textquotesingle ] \end{tabular}}}}%
    \put(0.20991809,0.36213786){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Izquierdo:[\textquotesingle Isocoria\textquotesingle , \textquotesingle Midriasis\textquotesingle ]\end{tabular}}}}%
    \put(0.20991809,0.35077424){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Derecho:  [\textquotesingle Miosis\textquotesingle , \textquotesingle Anisocoria\textquotesingle ]\end{tabular}}}}%
    \put(0.016641,0.38301062){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont [\textquotesingle Cefalea\textquotesingle , \textquotesingle Sincope\textquotesingle , \textquotesingle Incontinencia\textquotesingle ]\end{tabular}}}}%
    %to_fix

    %Medicamentos (to_fix)
    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont [\{ \textquotesin...\end{tabular}}}}%

@@

    \put(0.63928128,0.52831197){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont sdfg sdf sdfsd fsdf\end{tabular}}}}%
    \put(0.59572153,0.5272494){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%

@@

    \put(0.63928128,0.50503129){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont sd fsdf sdfsd sdf\end{tabular}}}}%
    \put(0.59572153,0.50399092){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%

@@

    \put(0.57282362,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont rsa asdfg sdfgdfs gdf\end{tabular}}}}%    

@@

    \put(0.57184628,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont sdfg dfgdf gdfg\end{tabular}}}}%    

@@

    \put(0.53910318,0.28131895){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%

@@

    \put(0.53965121,0.26504573){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%

@@

    \put(0.53965149,0.24893455){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%

@@

    \put(0.5709012,0.23278776){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%

@@

    \put(0.55290888,0.2166538){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%

@@

    \put(0.55094037,0.19532448){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%

@@

    \put(0.49140242,0.04639155){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA \end{tabular}}}}%

@@

    \put(0.48899072,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 12:31\end{tabular}}}}%
    \put(0.56346295,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 120\end{tabular}}}}%
    \put(0.62325414,0.62140804){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 121\end{tabular}}}}%
    \put(0.68836013,0.62140804){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 122\end{tabular}}}}%
    \put(0.74651878,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 123\end{tabular}}}}%
    \put(0.81241818,0.62140804){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 124\end{tabular}}}}%
    \put(0.87214411,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 125\end{tabular}}}}%
    \put(0.93275252,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 126\end{tabular}}}}%
    %Signos Vitales 2
    \put(0.48899072,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 12:41\end{tabular}}}}%

>>>>

\begin{document}
\fontfamily{lmss}\selectfont
    % Include Background in ./prescript/media/media/template_v1.pdf
    % \AddToShipoutPictureBG{\ifthenelse{\isodd{\value{page}}}{\includegraphics{laam_template}}{\includegraphics{laam_template}}}
    % Define page content
    %\textsf{\large{
    %\begin{changemargin}{1.5cm}{1.2cm}
        %\begin{enumerate}
            %
            %bla!
        %\end{enumerate}
    %         \put(1,1){\parbox[t]{3cm}{\textsf{\large{
    %    \textbf{Consulta \#:} 40
    % }
    % }}}
        % Indicaciones Extra
        % \begin{enumerate}
        %     \textbf{Indicaciones Extra: \\ } 
        % \end{enumerate}
    %\end{changemargin}
    %}}
    % \begin{picture}(1,0.77272727)%
    %     %Consulta    
    % \put(200,0){\parbox[t]{3cm}{\textsf{\large{
    %    \textbf40
    % }
    % }}}
    % \end{picture}
% \begingroup%
%   \makeatletter%
%   \providecommand\color[2][]{%
%     \errmessage{(Inkscape) Color is used for the text in Inkscape, but the package 'color.sty' is not loaded}%
%     \renewcommand\color[2][]{}%
%   }%
%   \providecommand\transparent[1]{%
%     \errmessage{(Inkscape) Transparency is used (non-zero) for the text in Inkscape, but the package 'transparent.sty' is not loaded}%
%     \renewcommand\transparent[1]{}%
%   }%
%   \providecommand\rotatebox[2]{#2}%
%   \newcommand\scaleInNode[1][1]{\tikzset{execute at begin node={\normalsize\larger[#1]}}}
%   \newcommand*\fsize{\dimexpr\f@size pt\relax}%
%   \newcommand*\lineheight[1]{\fontsize{\fsize}{#1\fsize}\selectfont}%
%   \ifx\svgwidth\undefined%
%     \setlength{\unitlength}{792bp}%
%     \ifx\svgscale\undefined%
%       \relax%
%     \else%
%       \setlength{\unitlength}{\unitlength * \real{\svgscale}}%
%     \fi%
%   \else%
%     \setlength{\unitlength}{\svgwidth}%
%   \fi%
%   \global\let\svgwidth\undefined%
%   \global\let\svgscale\undefined%
%   \makeatother%
%   \begin{picture}(1,0.77272727)%
%     \lineheight{1}%
%     \setlength\tabcolsep{0pt}%
%     \put(0,0){\includegraphics[width=\unitlength,page=1]{laam_template}}%

%     % \put(0.01140896,0.54355203){\parbox[t]{3cm}{\textsf{\large{
%     %    \textbf{Consulta \#:} 40
%     % }
%     % }}}
%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 40 }\end{tabular}}}}%
% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 40 }\end{tabular}}}}%
%    	\put(0.42718184,0.72336542){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ M011 }\end{tabular}}}}%
%     \put(0.3690564,0.69389968){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ SOPORTE }\end{tabular}}}}%
%     \put(0.39254546,0.6775768){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ QPR-002 }\end{tabular}}}}%

@@

    %Folio
    \put(0.91336785,0.68838718){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 40\end{tabular}}}}%

    \put(0.42638971,0.73960084){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 11\end{tabular}}}}%
    \put(0.43014479,0.72364315){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont M011\end{tabular}}}}%
   	\put(0.33829987,0.69381105){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont SOPORTE\end{tabular}}}}%
    \put(0.39132267,0.67728521){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont QPR-002\end{tabular}}}}%

    %Paciente
    \put(0.09655761,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont F55\end{tabular}}}}%
    \put(0.20912356,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 5556782349\end{tabular}}}}%
    \put(0.3268484,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Femenino\end{tabular}}}}%
    \put(0.42764439,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 5\end{tabular}}}}%
    \put(0.12766308,0.61324599){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Lillia Sanchez Jaime\end{tabular}}}}%
    \put(0.02575936,0.58169366){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%

    %Paciente desconocido
    \put(0.01999075,0.53033139){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
    \put(0.01999075,0.48794778){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont  NA\end{tabular}}}}%
    \put(0.09106678,0.46594263){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
    \put(0.12588643,0.44615019){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%

    %Padecimiento
    \put(0.0159714,0.1825995){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont este es el padecimiento actual \\fasd dasf asdklfnadskl; fn;klasdnfkl \\asdnfklsdnklf nsdklfn dklsnfklsdnf klsdnf klsdnf lksdnklf asdkl\textquotesingle af \\ nsdklfgn mklsdfnm l;sdknf lksdnfklsdnf lksdn\end{tabular}}}}%
    %\put(0.02265882,0.24439213){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont este es el padecimiento actual \\fasd dasf asdklfnadskl; fn;klasdnfkl asdnfklsdnklf nsdklfn dklsnfklsdnf klsdnf klsdnf lksdnklf asdkl\textquotesingle aff nsdklfgn mklsdfnm l;sdknf lksdnfklsdnf lksdn\end{tabular}}}}%

    %Generales
    \put(0.12027596,0.41209986){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA \end{tabular}}}}%
    \put(0.30209431,0.41082061){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA \end{tabular}}}}%
    \put(0.30209431,0.39566916){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA \end{tabular}}}}%
    %Trauma
    \put(0.21257984,0.38532216){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont \end{tabular}}}}%
    %Ojo Izquierdo
    \put(0.20991809,0.36213786){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Izquierdo: \end{tabular}}}}%
    %Ojo Derecho
    \put(0.20991809,0.35077424){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Derecho:  \end{tabular}}}}%
    \put(0.016641,0.38301062){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 
    \end{tabular}}}}%
    %to_fix
    %Via Aerea
    \put(0.01535741,0.34684125){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\end{tabular}}}}%

    %Medicamentos (to_fix)
    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont []\end{tabular}}}}%
    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont la medi\end{tabular}}}}%
    \put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont \end{tabular}}}}%

@@

    \put(0.63928128,0.52831197){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
    \put(0.59572153,0.5272494){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%

@@

    \put(0.63928128,0.50503129){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
    \put(0.59572153,0.50399092){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%

@@

    \put(0.57282362,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%    

@@

    \put(0.57184628,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%    

@@

    \put(0.53910318,0.28131895){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%

@@

    \put(0.53965121,0.26504573){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%

@@

    \put(0.53965149,0.24893455){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%

@@

    \put(0.5709012,0.23278776){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%

@@

    \put(0.55290888,0.2166538){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%

@@

    \put(0.55094037,0.19532448){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%

@@

    %\put(0.49140242,0.04639155){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA []\end{tabular}}}}%

@@

    %Signos Vitales 2
    %\put(0.48899072,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 12:41\end{tabular}}}}%
    %\put(0.56346295,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 220\end{tabular}}}}%
    %\put(0.62325414,0.59432876){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 321\end{tabular}}}}%
    %\put(0.68836013,0.59432876){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 422\end{tabular}}}}%
    %\put(0.74651878,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 523\end{tabular}}}}%
    %\put(0.81241818,0.59432876){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 624\end{tabular}}}}%
    %\put(0.87214411,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 725\end{tabular}}}}%
    %\put(0.93275252,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 826\end{tabular}}}}%
  \end{picture}
\endgroup%
\end{figure}
